Rusty Variation\\ Deadlock-free Sessions with Failure in Rust

### 2019-06-29 doc/ice2019/main.tex
Added a few lines about destructor bombs

Laumann \etal~\cite{jespersen2015} remark that they ``cannot prevent a channel value from being dropped prematurely''. They offer several solutions, but remark that each of these solutions are either insufficient, premature, or both. They note that the proposal to add linear types to Rust is currently postponed\footnote{\url{https://github.com/rust-lang/rfcs/pull/776}}, and that while \lstinline{#[must_use]} can be made to issue a warning if a value is dropped, it is ``easy to accidentally and purposely bypass''. Finally, they propose a compiler extension, developed in collaboration with Manish Goregaokar, \lstinline{humpty_dumpty}\footnote{\url{https://github.com/Manishearth/humpty_dumpty}}, ``which provides a lint that ensures that types annotated  with \lstinline{#[drop_protect]} are used linearly''. However, they note that \lstinline{humpty_dumpty} ``is still a work in progress, which by no means guarantees linearity in all cases''. No further work has been done on \lstinline{humpty_dumpty} since 2015.

>>>>

Laumann \etal~\cite{jespersen2015} remark that they ``cannot prevent a channel value from being dropped prematurely''. They offer several solutions, but remark that each of these solutions are either insufficient, premature, or both. They note that the proposal to add linear types to Rust is currently postponed\footnote{\url{https://github.com/rust-lang/rfcs/pull/776}}, and that while \lstinline{#[must_use]} can be made to issue a warning if a value is dropped, it is ``easy to accidentally and purposely bypass''. Finally, they propose a compiler extension, developed in collaboration with Manish Goregaokar, \lstinline{humpty_dumpty}\footnote{\url{https://github.com/Manishearth/humpty_dumpty}}, ``which provides a lint that ensures that types annotated  with \lstinline{#[drop_protect]} are used linearly''. However, they note that \lstinline{humpty_dumpty} ``is still a work in progress, which by no means guarantees linearity in all cases''. No further work has been done on \lstinline{humpty_dumpty} since 2015. The current version of the library enforces linearity \emph{dynamically}, using ``destructor bombs'', implemented by Manish Goregaokar\footnote{\url{https://github.com/Munksgaard/session-types/commit/0f25ccb7c3bc9f65fa8eaf538233e8fe344a189a}}. This technique hides a \lstinline{panic!} in channel destructors. Each invocation of \lstinline{close} then calls \lstinline{std::mem::forget}, bypassing the destructor bomb.
